Lactate transport inhibition therapeutically reprograms fibroblast

### 2024-02-20 manuscript/manuscript.qmd
start analysis of MIMS images

We were surprised to observe a relative paucity of metabolic changes in whole lung lysates following MCT inhibition compared to our *in vitro* studies. We hypothesized that this might be a consequence of the cellular heterogeneity of MCT expression in the fibrotic lung. To examine this hypothesis, we performed multi-isotope imaging mass spectrometry (MIMS) of mouse lungs following treatment with ^15^N-proline and ^2^H-glucose. MIMS enables the quantification of stable isotope tracer uptake into tissue biomass with subcellular spatial resolution [@steinhauser2012; @narendra2020]. For three days prior to tissue collection, mice received twice daily intraperitoneal injections of 5 mg ^15^N-proline as a tracer for tissue fibrosis and 50 mg ^2^H-glucose as a metabolic tracer. Lung tissue sections were subsequently imaged by nanoscale seconary ion mass spectrometry to quantify spatially resolved isotope tracer uptake (**Figure 9B**).

>>>>

We were surprised to observe a relative paucity of metabolic changes in whole lung lysates following MCT inhibition compared to our *in vitro* studies. We hypothesized that this might be a consequence of the cellular heterogeneity of MCT expression in the fibrotic lung. To examine this hypothesis, we performed multi-isotope imaging mass spectrometry (MIMS) of mouse lungs following treatment with ^15^N-proline and ^2^H-glucose. MIMS enables the quantification of stable isotope tracer uptake into tissue biomass with subcellular spatial resolution [@steinhauser2012; @gyngard2019]. For three days prior to tissue collection, mice received twice daily intraperitoneal injections of 5 mg ^15^N-proline as a tracer for tissue fibrosis and 50 mg ^2^H-glucose as a metabolic tracer. Lung tissue sections were subsequently imaged by nanoscale secondary ion mass spectrometry to quantify spatially resolved isotope tracer uptake (**Figure 9B**).
